Erratum: Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae [Phys.~Rev.~D 105, 063006 (2021)]

### 2021-11-08 erratum/ccsn_erratum.tex
Fig1 & Fig3 redone + Table 2 updated

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 18 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. We have not made the distinction between the different simulations since we are only interested in the relationship between the variables.
 \pcd{[RATIO SHOULD BE MULTIPLIED BY A FACTOR 2 IN THE PLOT]}
 }
 \label{fig:LMVAR}
\end{figure}

\begin{table}[h]
 \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 2.00 \times 10^{-06}$ & $4.24 \times 10^{-08}$ \\   
   $\beta_2$  &  $-1.64 \times 10^{-9}$ & $1.00 \times 10^{-10}$ \\
   $\beta_3$  &  $ 2.02 \times 10^{-12}$ & $5.40 \times 10^{-14}$ \\
   $\alpha_0$ &  $-9.51 \times 10^{+00}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.\pcd{[CHECK IF NUMBERS ARE CORRECT]}}\label{tab:model}
\end{table}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Comparison of the time evolution of the ratio $M_{\rm PNS}/R_{\rm PNS}^2$ estimated from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (shown by open triangles and by the 95\% confidence belt in grey) against the value derived from the PNS mass and radius given by the simulation code (shown by filled black circles). The size of the triangles are represented proportionally to the magnitude of the $\mbox{}^2 g_2$-mode frequency estimates. \pcd{[RATIO SHOULD BE MULTIPLIED BY A FACTOR 2 IN THE PLOT]}}
 \label{fig:ratio}
\end{figure}

>>>>

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 18 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. We have not made the distinction between the different simulations since we are only interested in the relationship between the variables.}

 \label{fig:LMVAR}
\end{figure}

\begin{table}[h]
 \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 2.00 \times 10^{-06}$ & $4.23 \times 10^{-08}$ \\   
   $\beta_2$  &  $-1.64 \times 10^{-9}$ & $9.99 \times 10^{-11}$ \\
   $\beta_3$  &  $ 2.03 \times 10^{-12}$ & $5.41 \times 10^{-14}$ \\
   $\alpha_0$ &  $-9.54 \times 10^{+00}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.}\label{tab:model}
\end{table}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Comparison of the time evolution of the ratio $M_{\rm PNS}/R_{\rm PNS}^2$ estimated from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (shown by open triangles and by the 95\% confidence belt in grey) against the value derived from the PNS mass and radius given by the simulation code (shown by filled black circles). The size of the triangles are represented proportionally to the magnitude of the $\mbox{}^2 g_2$-mode frequency estimates. }
 \label{fig:ratio}
\end{figure}
